---
title: "Lab10"
author: "Lingchen Lou"
date: "2018/11/21"
output: pdf_document
---
# Question 1

Write a function that calculates cumulative distribution function of a binomial random variable. Compare results from your function with pbinom() function.

```{r}
pbinom1 <- function(x, n, p){
    te.result=0
    for (i in 0:x){
      te.result<-te.result+dbinom(i,n,p)
    }
    return(te.result)
}
pbinom1(2, 10, 0.5)
pbinom(2, 10, 0.5)

```
Those two results are excataly the same.

# Question 2

Write a function that runs simulations to obtain power from a one-sample t-test. Run your function (with number of simulations = 10,000 ) with n = 30, delta = 0.5, sd = 1 and sig.level = 0.05. Compare your results with power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = ???one.sample???).

```{r}
power<-function(n, delta, sd, sig.level = 0.05, type = 'one.sample',simulation=10000){
  counter=0
  for(i in 1:10000){
    x <- rnorm(n,delta,sd)
    p_value<-t.test(x)$p.value
    if(p_value< sig.level) {
      counter <- counter + 1 }
  }
  return(counter/simulation)
}
power(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = 'one.sample')
power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = 'one.sample')
```
Those two results are similar.